Lies and the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)

### 2018-10-31 GSV-comment-brief.Rmd
Update readme and Rmd

---
title: "Lies and the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)"
author: "David Hugh-Jones"
date: "`r Sys.Date()`"
output:
  bookdown::tufte_html2: 
    pandoc_args: ['--self-contained']
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: 
    pandoc_args: ['--self-contained']
bibliography: bibliography.bib
link-citations: yes
---

@@

nreps <- 1000L
rewrite_csv <- FALSE # set to TRUE to (re)create the simulations CSV file
cache_results <- FALSE # FALSE to recalculate all results. TRUE for speed.
```

@@

One can then calculate the proportions of liars as $L/N$. Note that we are now directly estimating
how many liars are in the whole sample $N$, where a liar is someone who always reports heads. From
this, one can derive confidence intervals and expected values in the usual way.

>>>>

---
title: "Lies and the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)"
author: "David Hugh-Jones"
date: "`r Sys.Date()`"
output:
  bookdown::tufte_html2: 
    pandoc_args: ['--self-contained']
    keep_intermediates: true
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  bookdown::tufte_book2:
    citation_package: natbib
    latex_engine: xelatex
    md_extensions: +raw_attribute
bibliography: bibliography.bib
link-citations: yes
abstract: |
  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution   of the number of liars in "coin flip" style experiments. However, their method gives 
  erroneous confidence intervals. I explain why and describe two better
  ways to calculate probability distributions.
---

@@

nreps <- 1000L
rewrite_csv <- FALSE # set to TRUE to (re)create the simulations CSV file
cache_results <- TRUE # FALSE to recalculate all results. TRUE for speed.
```

@@

One can then calculate the proportions of liars as $L/N$. Note that we are now directly estimating
how many liars are in the whole sample $N$, where a liar is someone who always reports heads. From
this, one can derive confidence intervals and expected values in the usual way.^[R code to
run these calculations is available at https://github.com/hughjonesd/GSV-comment.]
